Transactions Fraud Detection using Machine Learning and Nature Inspired Algorithms

### 2020-05-27 paper/main.tex
Add abstract to paper

\begin{document}
%
\title{Transactions Fraud Detection using Machine Learning and Nature Inspired Algorithms}
%
%\titlerunning{Abbreviated paper title}
% If the paper title is too long for the running head, you can set
% an abbreviated paper title here
%
\author{Peter Mačinec \and Timotej Zaťko}
%
\authorrunning{Peter Mačinec, Timotej Zaťko}
% First names are abbreviated in the running head.
% If there are more than two authors, 'et al.' is used.
%
\institute{Faculty of Informatics and Information Technologies,\\Slovak University of Technology, Bratislava}
%
\maketitle              % typeset the header of the contribution
%
\begin{abstract}
The abstract should briefly summarize the contents of the paper in
15--250 words.

\keywords{Transactions Fraud Detection \and Machine Learning \and Nature Inspired Algorithms \and Data Analysis.}
\end{abstract}
%
%
%
\section{Introduction}

@@

% TODO: pribuzne prace na feature selection
% TODO: spomenut pouzite algoritmy
% TODO: spomenut domeny, datasety, charakteristky datasetov

% Required: Podobné práce / Related Work - ako riešili vašu alebo podobnú úlohu v
% existujúcich prácach - nezabudnite v texte uvádzať citácie na práce.

@@

- Gray Wolf Optimization Algorithm \cite{Mirjalili_Mirjalili_Lewis_2014}

>>>>

\begin{document}
%
\title{Transactions Fraud Detection using Machine Learning and Nature Inspired Algorithms}
%
\titlerunning{Transactions Fraud Detection using ML and NIA}
% If the paper title is too long for the running head, you can set
% an abbreviated paper title here
%
\author{Peter Mačinec \and Timotej Zaťko}
%
\authorrunning{Peter Mačinec, Timotej Zaťko}
% First names are abbreviated in the running head.
% If there are more than two authors, 'et al.' is used.
%
\institute{Faculty of Informatics and Information Technologies,\\Slovak University of Technology, Bratislava}
%
\maketitle              % typeset the header of the contribution
%
\begin{abstract}
Credit card payments are still more and more preferred because of convenience. People are using credit cards to pay not only at stores, but also in e-shops. However, with the rise of credit cards usage, suitable environment for frauds in transactions arises. The data of transactions are usually collected by the banks, that indicates usage of data-mining approaches to prevent frauds. The performance of model is based on several sub-steps and decisions, like data analysis, preprocessing, feature selection and hyperparameter optimization. In the area of transactions fraud detection, datasets usually contain a lot of features (several hundreds) that are however mostly anonymized. Thus we decided to focus on improving model mainly by selecting appropriate features using nature inspired algorithms. Nature inspired algorithms proved to be powerful methods in such optimization tasks. Experiments showed that proper combination of machine learning model with feature selection using nature inspired algorithms has potential to help to prevent transaction frauds.

\keywords{transactions fraud detection \and machine learning classification \and nature inspired algorithms \and feature selection \and bat algorithm.}
\end{abstract}
%
%
%
\section{Introduction}

@@

@@
